 \documentclass[11.8pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
%/usr/local/texlive/2015/texmf-dist/tex/latex/moderncv

\newcounter{publishcount}
\stepcounter{publishcount}

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.86]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Kevin} % Your first name
\familyname{Wang PhD} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Data Scientist and Statistician}
%\address{Room 807, School of Mathematics and Statistics, Carslaw Building (F07)}{University of Sydney, NSW, Australia 2006}
\mobile{(+61) 404 955 255}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{kevinwangstats@gmail.com}
%\email{kevin.wang@sydney.edu.au}
\homepage{Portfolio: kevinwang09.github.io}{} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{Nationality: Australian}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%----------------------------------------------------------------------------------------

\begin{document}

	
%	\clearpage
%	
%	\recipient{HR Manager}{Company} % Letter recipient
%	\date{\today} % Letter date
%	\opening{Dear HR Manager} % Opening greeting
%	\closing{Sincerely yours, } % Closing phrase
%	\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%	
%	\makelettertitle % Print letter title
%
%
%Thank you for considering my application,
%	
%	\makeletterclosing % Print letter signature
%	
%	\clearpage
%	
%	\makecvtitle % Print the CV title

\makecvtitle % Print the CV title
	
%Passionate data scientist with a PhD in statistics and a proven track record of delivering valuable analytical insights. I am a highly effective communicator with numerous awards. I am highly skilled in developing machine learning models using the \texttt{R} language. 

%\section{Profile}
%
%
%Kevin is a research associate with a PhD in statistics from the University of Sydney in Australia. His main interest lies in the use of statistics and data science to uncover expected patterns in data to ultimately inform decision making. In his current role, his work focuses on statistical modelling of complex biological data and he provides consultations and analytical insights in various scientific fields. However, his specialisation in predictive modelling and applied statistical computation are applied broadly for data under any context. Kevin is a passionate and innovative data scientist and he loves talking with domain experts over whatever data problems they have on hand. His strong communication skills have been awarded with numerous prizes and scholarships throughout his career. 


\section{Experience}
	\cventry{Present \\ 2020 Jul}{Statistician (data scientist)}{CSL Behring}{Australia}{}{
	CSL is the largest biotechnology company in Australia, manufacturing plasma protein derivatives and vaccines. Selected work responsibilities:
	\begin{itemize}
		\item Using statistical process control techniques to standardise manufacturing and quality control laboratory procedures with engineers and biochemists.
		\item Using innovative machine learning models and R-Shiny dashboards to identify areas of improvement, automate routine procedures and speed up turnaround time for QC and manufacturing. 
		\item Biostatistical support for R\&D of new products, including high-value products like coronavirus vaccines and treatments. 
		\item Design experiments and methodologies to understand the chemical stability of products, conform to regulatory requirements and ensure product effectiveness. 
		\item Achieved savings of multiple batches of plasma products, with some batch valued up to \$1M.
	\end{itemize}
}

	\cventry{2020 Jun \\ 2019 Sep}{Research Associate}{University of Sydney}{}{}{
		\begin{itemize}
			\item The major research project developed a framework for clinical outcome prediction for individual patients using genomics data. Melanoma was a key focus of this research and the key biomarkers were validated and implemented on a cost-effective bioassay. 
			\item \texttt{R} software packages associated with the research were developed and maintained in a reproducible environment. 
			\item Visiting scholar at Cornell University for 2 months and delivered a workshop in open-source single-cell analytics using Cloud technology. 
			\item Published peer-reviewed articles in top-tier journals covering a wide range of topics in cancer and public health.
		\end{itemize}	
	}
	
	\cventry{2019 Mar \\ 2016 Mar}{Postgraduate Teaching Fellow}{University of Sydney}{}{}{
		\begin{itemize}
		\item Delivered lectures (200+ students) and tutorials, covering 15 different courses, including statistics, mathematics and data science. Achieved ~85\% satisfactory rating for end-of-course surveys. 
		\item Authored and designed course content at both the undergraduate and postgraduate levels.
		\item Mentored and trained new statistics tutors.
%		\item This position is equivalent to an Associate Lecturer at 0.2 full-time load.
		\end{itemize}	
	}
	
	
	%		\begin{itemize}
	%	\item MATH1001: Differential Calculus
	%	\item MATH1005: Statistics (four times)
	%	\item MATH1015: Biostatistics 
	%	\item MATH1905: Statistics (Advanced)
	%	\item MATH2069: Discrete Mathematics and Graph Theory
	%	\item PHAR1811: Foundation of Pharmacy (Statistics copmonent)
	%	\item PHAR2813: Therapeutic Principles (Mathematics and Statistics components)
	%	\item STAT2911: Probability Theory (Advanced)
	%	\item STAT2912: Statistical Tests (Advanced)
	%	\item STAT3914: Applied Statistics (Advanced)
	%	\item STAT5002: Introduction to Statistics (Master of IT core component)
	%	\item STAT5003: Computational Statistical Methods (Master of IT core component)
	%	\end{itemize} 
	%



\section{Education}

\cventry{2016--2020}{Doctor of Philosophy in Science}{University of Sydney}{}{}{
	\begin{itemize}
		\item The PhD research was on statistical bioinformatics. 
		\item Statistical machine learning methods were developed to solve specific challenges in individual patient clinical outcome predictions and thereby enabling personalised medicine. 
		\item Real-world biomedical data from collaborators were used to motivate and articulate important challenges in current statistical research. The value of this thesis is the synthesis of statistics, clinical implementation and practical deployment. 
	\end{itemize}
}

\cventry{2012-2015}{Bachelor of Science (Adv. Mathematics) (Hon. I)}{University of Sydney}{}{}{
	\begin{itemize}
		\item Major in statistics and financial mathematics.
		\item The Honours thesis examined functional MRI data and the inferred brain connectivity networks through the use of different statistical association measures. 
	\end{itemize}
} 

\clearpage
\section{Skills}

%	\subsection{Technical}
\cvitem{Applied statistics}{Highly experienced at the research level and consulting level. Ability to transform business and cross-disciplinary problems into a statistical framework to deliver solutions. Strong experience with model selection to extract explainable insights from data.}

\cvitem{Statistical modelling}{Highly experienced at the research level and consulting level. Specialisation in predictive modelling for high-dimensional data such as genomics data with 20k+ features.}

\cvitem{\texttt{R} \& \texttt{git}}{Highly proficient in scripting under a reproducible environment. Strong ability to use \texttt{tidyverse} and \texttt{shiny} to deal with dirty data and produce visualisations and presentable insights. Ability to combine git together with unit testing, continuous integration and coverage testing. Author and maintainer of several open-source \texttt{R} packages, including \texttt{APES}, \texttt{mcvis} and \texttt{scMerge}.}

\cvitem{\texttt{python} \& \texttt{SQL}}{Proficient in writing scripts and notebooks. Experience in \texttt{pandas}, \texttt{numpy}, \texttt{scikit-learn} and \texttt{keras} for personal interest projects on GitHub.}

\cvitem{docker \& Cloud}{Proficient in building docker images and deployment through Google Cloud. Experience in holding reproducible workshops using both with excellent participant feedback.}


%	\subsection{Communication}
%	
%	\cvitem{Consulting}{
%		I have collaborated with researchers from different scientific fields and provided important analytical insights. These work eventually lead to publications in peer-reviewed journals.
%	}
%	
%	\cvitem{Workshop}{
%		I have designed and delivered workshops for both industry and academic professionals on statistics and \texttt{R}. These workshops are about 30+ attendees in size and I received an Google Cloud for Education grant worth of 2,000 AUD.
%	}
%	
%	\cvitem{Mentoring}{
%		I have mentored and trained statistics tutors at USYD and supervised an overseas student on a statistics project. 
%	}
%	
	
	
	
	\section{Volunteering}
	\cventry{Present \\ 2021}{Communication officer}{Statistical Society of Australia, Victorian branch}{}{}{Managing communications and social media accounts. Organising events and workshop for the society.}
	
%	\cventry{2016-2019}{Outreach volunteer}{University of Sydney}{}{}{Delivered seminars and hands-on workshops for visiting high school and university students.
%		\begin{itemize}
%			%		\item Long-term participant of the outreach program at the School of Mathematics and Statistics. 
%%			\item 
%%			\item Previously a board member of the School Outreach committee.
%			%		A short abstract of my research on the USYD website is  \href{https://sydney.edu.au/science/news-and-events/2018/12/13/4-cool-topics-you-can-study-in-maths.html?fbclid=IwAR3I3pYHL-yBls__Rt0izDf_wguMjVVEIiK26Vu58j6XneF1Ixn5ZjZhbMk}{here}.
%		\end{itemize}
%	}
	
	\cventry{2017}{President}{Sydney University Mathematics Society}{}{}{Oversaw finances of the Society, organised academic/industry events and negotiated coporate sponsorships for three years before the presidency in 2017. Delivered seminars and hands-on workshops for visiting high school and university students.
%		\begin{itemize}
%			\item 
%			\item Organising speakers for industry and academic seminars and social events. 
%			\item Management of social media accounts, operations and sales of merchanise.
			%		\item Previous positions held: Vice President, Treasurer and Social Director. 
			%\item Oct 2016 - \emph{``Primes, Poisson, and Pok\'{e}mons."}
			%\item Oct 2016 - \emph{``The Pok\'{e}mon Collector's Problem: A Simulation Study Based on Theoretical Modesl and Applied Methods."}
			%\item Aug 2015 - \emph{``An Application of PCA to Cricket Data and General Practice of Statistics''}
			%\item Apr 2015 - \emph{``Model Selection and Model Averaging --- Danger of Certainty in Statistics''}
			%\item May 2014 - Presentation on \emph{``An Algorithm To Achieve Optimality And Stability of Marriages and College Admission.''}
%		\end{itemize}
	}
	
	
%	\cventry{2015}{President}{Sydney University Statistics Society}{}{}{Organised academic/industry events and negotiating coporate sponsorships.
%		\begin{itemize}
%			\item 
			%\item April 2015: organising introductory SAS software workshop. 
			%\item In September 2015, we invited founder of Prioma Capitals for careers talk. 
%		\end{itemize}
%	}
	
	\section{Scholarships \& Awards}
	\cventry{2019}{Statistical Society of Australia, NSW}{JB Douglas Award (joint runner-up). Competitive prize awarded to the top statistics research PhD candidates in New South Wales. AUD 250}{}{}{}
	\cventry{2019}{Statistical Society of Australia}{Golden Jubilee Travel Grant. Competitive funding for a statistics PhD candidate in Australia. AUD 1,000}{}{}{}
%	\cventry{2018}{Sydney Bioinformatics Research Symposium}{Best poster presentation at the conference. AUD 50}{}{}{}
	\cventry{2017}{International Biometric Society -  Australasian Region}{Best student talk at the biennial conference. AUD 500}{}{}{}
%	\cventry{2017 \& 2018 }{Australian Bioinformatics \& Computational Biology Society}{Travel scholarship to ABACBS annual conference. AUD 250}{}{}{}
	\cventry{2016-2020}{Australian Postgraduate Award}{For the duration of the PhD program at the University of Sydney. AUD 26,288 p.a}{}{}{}
	\cventry{2016}{Charles Perkins Centre}{Summer Research Scholar in Bioinformatics. Research in data visualisation, focus on gene interaction networks for cancers. AUD 2,400}{}{}{}
	\cventry{2015}{International Biometric Society - Australasian Region}{Awarded to the top biostatistics student undertaking a Honours program in AU/NZ region. AUD 1,500}{}{}{}
	\cventry{2014}{Australian National University}{Summer Research Scholar in Mathematical Statistics. Research in statistical model selection and averaging techniques. AUD 3,000}{}{}{}
	\cventry{2013}{Winston Charitable Foundation}{Research Internship in Mathematical Biology. Research in mathematical modelling in the spread of infectious parasites in beehives. AUD 2,000}{}{}{}

\newpage
\section{Publications} \label{sec: publication}
	
	\cvitem{\thepublishcount}{Schafer, S., \textbf{Wang, K. Y. X.}, Sundling, F., Yang, J.Y.H., \& Liu, A. \textbf{2021}. Modelling maternal and perinatal risk factors to predict poorly controlled childhood asthma. \textit{PLOS ONE}, (in press).}
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{
		Kim J.H., \textbf{Wang, K. Y. X.}, Chen, C., Lin, Y., Tam, P.P.L., Lin, D.M., Yang, J.Y.H., \& Yang, P. \textbf{2021}. Cepo uncovers cell identity through differential stability. (Under review).}
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{
		Lin, C., \textbf{Wang, K. Y. X.}, \& Mueller, S. \textbf{2020}. mcvis: A new framework for collinearity discovery, diagnostic and visualization. \textit{Journal of Computational and Graphical Statistics}, 1-13.}	
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{Hewavisenti, R., Ferguson, A., \textbf{Wang, K. Y. X.}, Jones, D., Gebhardt, T., Edwards, J., Zhang, M., Britton, W., Yang, J., Hong, A., \& Palendira, U. \textbf{2020}. CD103+ tumour-resident CD8+ T cell numbers underlie improved patient survival in oropharyngeal squamous cell carcinoma. \textit{Journal for ImmunoTherapy of Cancer}, 8:e000452.}
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{
		\textbf{Wang, K.Y.X.}, Tarr, G., Yang, J.Y.H., Mueller, S. \textbf{2019}. Fast and approximate exhaustive variable selection for generalised linear models with APES,  Invited paper to \textit{Australia \& New Zealand Journal of Statistics}, 61 (4) 445-465.}
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{
		Lin, Y., Ghazanfar, S., \textbf{Wang, K.Y.X.}, Gagnon-bartsch, J.A., Lo, K.K., Han, Z., Ormerod, J.T., Speed, T.P., Yang, P., Yang, J.Y.H. \textbf{2019}. scMerge: Leveraging factor analysis, stable expression and pseudo-replication to merge multiple single-cell RNA-seq data, \textit{Proceedings of the National Academy of Sciences of the United States of America}, 116 (20) 9775-9784.}	
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{Pires da Silva, I., \textbf{ Wang, K.Y.X.}, Wilmott, J.S., Holst, J., Carlino, M.S., Park, J.J., Quek, C., Wongchenko, M., Yan, Y., Mann, G., Johnson, D.B., McQuade, J.L., Rai, R., Kefford, R.F., Rizos, H., Scolyer, R.A., Yang, J.Y.H., Long, G. V, Menzies, A.M. \textbf{2019}. Distinct molecular profiles and immunotherapy treatment outcomes of V600E and V600K BRAF-mutant melanoma. \textit{Clinical Cancer Research}, 25 (4) 1272-1279.}
	
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{\textbf{Wang, K.Y.X}., Menzies, A.M., Silva, I.P., Wilmott, J.S., Yan, Y., Wongchenko, M., Kefford, R.F., Scolyer, R.A., Long, G. V, Tarr, G., Mueller, S., Yang, J.Y.H. \textbf{2019}. bcGST - an interactive bias-correction method to identify over-represented gene-sets in boutique arrays. \textit{Bioinformatics}, 35 (8) 1350-1357.}
	
	\cvitem{\stepcounter{publishcount} \thepublishcount}{Strbenac, D., \textbf{Wang, K.Y.X.}, Wang, X., Dong, J., Mann, G.J., Mueller, S., Yang, J.Y.H. \textbf{2019}. Melanoma Explorer: a web application to allow easy reanalysis of publicly available and clinically-annotated melanoma omics datasets. \textit{Melanoma Research}.}
	%
	
	
	%\cvitem{\LaTeX}{Highly proficient. Written extensive university materials using \LaTeX. Designed and delivered workshop for university  undergraduates.}
	%\cvitem{Mathematica\\MATLAB/Julia \\ Tablaeu}{Working knowledge.}
	

	
	%----------------------------------------------------------------------------------------
	
	
	
	%----------------------------------------------------------------------------------------
	%	LANGUAGES SECTION
	%----------------------------------------------------------------------------------------
	%\clearpage
	
	%\section{Miscellaneous}
	%
	%
	%\section{Professional society memberships}
	%\cvitem{}{
	%\begin{itemize}
	%\item Australian Bioinformatics \& Computational Biology Society
	%\item International Biometric Society (Australasian Region)
	%\item Royal Statistical Society
	%\item Statistical Society of Australia
	%%\item International Educational Data Mining Society. 
	%\end{itemize}
	%}
	
	
	
	%
	\section{Seminars}
	\cvitem{Workshop}{
	\begin{itemize}
		\item \textit{"Single-cell RNA-Seq analysis from beginning to end"} at Hong Kong University (2019), Sydney University (2019) and Cornell University (2020).
		\item \textit{"Enter the Tidyverse with R and RStudio"} at BioinfoSummer (2019).
		\item \textit{"Fast algorithms and modern visualisations for feature selection"} at Joint International Society for Clinical Biostatistics and Australian Statistical Conference (2018). 
	\end{itemize}
	}

	
	\cvitem{Talks}{
	\begin{itemize}
		\item 2019 International Conference on Econometrics and Statistics (invited)
		\item 2019, 2017 International Biometrics Society - Australasian Region Conference
		\item 2018 Australian Bioinformatics \& Computational Biology Society Conference
		\item 2018 Joint Statistical Meeting
		\item 2017 International Conference in Robust Statistics 
		\item 2016 Australian Statistical Conference
	\end{itemize}		
	}
	
	
%\section{Teaching}
%\hspace{2.6cm} Courses are listed below with lecturing duties highlighted in \textbf{bold}: \\ 
%\cvitem{Undergraduate}{DATA1001: Foundation of Data Science (\textbf{2018 S2})}
%	\cvitem{}{DATA1901: Foundation of Data Science (Adv) (2019 S1)}
%	\cvitem{}{DATA2902:  Learning from Data (Adv) (2019 S2)} 
%	\cvitem{}{MATH1001: Differential Calculus (2016 S1)}
%	\cvitem{}{MATH1005: Statistics (\textbf{2015 WS}, S2; 2016 SS, WS; \textbf{2017 S2}, SS)
%	}
%	\cvitem{}{MATH1015: Statistics (2015 S1, \textbf{2018 S1})
%	}
%	\cvitem{}{MATH1115: Interrogating Data (2019 S1)}
%	\cvitem{}{MATH1905: Statistics (Adv) (2016 S2)
%	}
%	\cvitem{}{MATH2069: Discrete Mathematics and Graph Theory (2016 S1)
%	}
%	\cvitem{}{PHAR1811: Foundation of Pharmacy (2016 S1)
%	}
%	\cvitem{}{PHAR2813: Therapeutic Principles (2016 S1)
%	}
%	\cvitem{}{STAT2911: Probability Theory (Adv) (2017 S1)
%	}
%	\cvitem{}{STAT2912: Statistical Tests (Adv) (2016 S2)
%	}
%	\cvitem{}{STAT3914: Applied Statistics (Adv) (\textbf{2016 S2})
%	}
%	
%	\cvitem{Postgraduate}{STAT5002: Introduction to Statistics (2017 S1; \textbf{2018 S1})
%	}
%	\cvitem{}{STAT5003: Computational Statistical Methods (2016 S2; \textbf{2017 S2})
%	}
	
	
	
	
%	\cvitem{Poster}{
%		\begin{itemize}
%			\item 2016, 2017, 2018 Sydney Bioinformatics Research Symposium
%			\item 2016, 2017 Australian Bioinformatics \& Computational Biology Society Conference 
%			\item 2016 Sydney Cancer Conference
%			\item 2015 AMSI BioInfo Summer
%		\end{itemize}	
%	}


%	
%	\cventry{2012-2013}{Mathematics Special Studies Program(SSP)}{}{}{}{
%	Invited into the prestigious SSP in University of Sydney. These are special courses for selected students to learn about advanced topics and develop professional mathematical communication and presentation skills.
%	\begin{itemize}
%	\item MATH2917 Project: Proof of Alternating Matrices Conjecture --- Jacobi's Triple Product Identity and Euler's Pentagonal Number Theorem, Ramanujan's Congruences of Partition Function. \url{http://goo.gl/tUkCAe}
%	\item MATH2916 project: Calculus of Variation --- Optimizations and Isoperimetric Constraints on Functionals. \url{http://goo.gl/3VcbZN}
%	\end{itemize}
%	}
	
	
	%
	%\section{Miscellaneous}
	%\cvitem{Language}{English, Mandarin, Cantonese}
	%
	%\cvitem{Citizenship}{
	%Australian citizen
	%}
	
	
	
	
	
	%----------------------------------------------------------------------------------------
	%	INTERESTS SECTION
	%----------------------------------------------------------------------------------------
	
	%----------------------------------------------------------------------------------------
	%	COVER LETTER
	%----------------------------------------------------------------------------------------
	
	% To remove the cover letter, comment out this entire block
	
	
	%----------------------------------------------------------------------------------------
	
\end{document}