 \documentclass[12pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
%/usr/local/texlive/2015/texmf-dist/tex/latex/moderncv

\newcounter{publishcount}
\stepcounter{publishcount}

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.86]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Kevin Y.X.} % Your first name
\familyname{Wang} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Statistician and Data Scientist}
%\address{Room 807, School of Mathematics and Statistics, Carslaw Building (F07)}{University of Sydney, NSW, Australia 2006}
\mobile{(+61) 404 955 255}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{kevin.wang09@gmail.com}
%\email{kevin.wang@sydney.edu.au}
\homepage{kevinwang09.github.io/}{} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{https://github.com/kevinwang09. Updated on \today}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%----------------------------------------------------------------------------------------

\begin{document}
	
	\makecvtitle % Print the CV title
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	
%	Passionate data scientist with a PhD in statistics and a proven track record of delivering valuable analytical insights. I am a highly effective communicator with numerous awards for research presentations and worked as a part-time lecturer at the University of Sydney. I am highly skilled in developing machine learning predictive models using the \texttt{R} language. 


\section{Profile}


Kevin is a research associate with a PhD in statistics from the University of Sydney in Australia. His main research interest lies in the use of statistics and bioinformatics to uncover expected patterns in health data to ultimately inform decision making. In his current role, his work focuses on statistical modelling of complex biological data and he provides consultations and analytical insights in various scientific fields. His specialisation in predictive modelling and applied statistical computation are applied broadly for data under any context. Kevin is a passionate and innovative data scientist and he loves talking with domain experts over whatever data problems they have on hand. His strong communication skills have been awarded with numerous prizes and scholarships throughout his career. 


\section{Experience}

	\cventry{2019--2020}{Research Associate}{University of Sydney}{}{}{
		\begin{itemize}
			\item Developed a clinically implementable prediction model using genomics data with clinicians and biologists.
			\item Developed and maintained open-sourced \texttt{R} software packages.
			\item Designed and hosted cloud-based workshops.
		\end{itemize}	
	}
	
	\cventry{2016--2019}{Postgraduate Teaching Fellow}{University of Sydney}{}{}{
		\begin{itemize}
			\item Authored lecturing materials for courses at both undergraduate and postgraduate level with strong positive student feedback. 
			\item Delivered lectures (200+ students) and tutorials, covering 15 different courses, including statistics, mathematics and data science.
			%	\item Equivalent to an Associate Lecturer at 0.2 full-time load.
			\item Mentored and trained new statistics tutors.
		\end{itemize}	
	}
	
	\cventry{2016}{Summer Research Scholar in Bioinformatics}{Charles Perkins Centre}{}{}{
	Research in data visualisation, focus on gene interaction networks for cancers (3 months)}
	
	\cventry{2015}{Summer Research Scholar in Mathematical Statistics}{Australian National University}{}{}{Research in statistics, particularly on model selection and averaging techniques (3 months)}
	
	\cventry{2013}{Research Internship in Mathematical Biology}{Winston Charitable Foundation}{}{}{Research in mathematical modelling of the spread of infectious parasites in beehives (2 months)}
	
	
	%		\begin{itemize}
	%	\item MATH1001: Differential Calculus
	%	\item MATH1005: Statistics (four times)
	%	\item MATH1015: Biostatistics 
	%	\item MATH1905: Statistics (Advanced)
	%	\item MATH2069: Discrete Mathematics and Graph Theory
	%	\item PHAR1811: Foundation of Pharmacy (Statistics copmonent)
	%	\item PHAR2813: Therapeutic Principles (Mathematics and Statistics components)
	%	\item STAT2911: Probability Theory (Advanced)
	%	\item STAT2912: Statistical Tests (Advanced)
	%	\item STAT3914: Applied Statistics (Advanced)
	%	\item STAT5002: Introduction to Statistics (Master of IT core component)
	%	\item STAT5003: Computational Statistical Methods (Master of IT core component)
	%	\end{itemize} 
	%



\section{Education}

\cventry{2016--2020}{Doctor of Philosophy in Science}{University of Sydney}{}{}{
	\begin{itemize}
		\item Research in statistics and bioinformatics.
		\item The PhD thesis develops methods to enable prediction of patient clinical outcomes using omics data under a rigorous statistical framework.
		%	\item Other related collaboration projects covered a range of scientific problems relating to biological heterogeneity in cancer.
	\end{itemize}
}

\cventry{2012-2015}{Bachelor of Science (Adv. Mathematics) (Hon. I)}{University of Sydney}{}{}{
	\begin{itemize}
		\item Major in statistics and financial mathematics.
		\item The Honours thesis examines the effect of different measures of association in human brain connectivity modelling utilising functional MRI data.
	\end{itemize}
} 
	
	\section{Skills}
	
%	\subsection{Technical}
	\cvitem{Applied statistics}{Highly experienced at the research level. Specialisation in predictive modelling.
%		Publications in top journals, including \textit{Bioinformatics}, \textit{Clinical Cancer Research} and \textit{PNAS}.
	}

	\cvitem{\texttt{R} \& \texttt{git}}{Highly proficient in scripting, \texttt{tidyverse}, \texttt{shiny} and package development with unit testing, continuous integration and coverage testing.}
	
	\cvitem{\texttt{docker} \& Google Cloud}{Proficient in building docker images and deployment through Google Cloud.}
	
	\cvitem{\texttt{python} \& \texttt{SQL}}{Working knowledge in writing basic scripts.}

%	\subsection{Communication}
%	
%	\cvitem{Consulting}{
%		I have collaborated with researchers from different scientific fields and provided important analytical insights. These work eventually lead to publications in peer-reviewed journals.
%	}
%	
%	\cvitem{Workshop}{
%		I have designed and delivered workshops for both industry and academic professionals on statistics and \texttt{R}. These workshops are about 30+ attendees in size and I received an Google Cloud for Education grant worth of 2,000 AUD.
%	}
%	
%	\cvitem{Mentoring}{
%		I have mentored and trained statistics tutors at USYD and supervised an overseas student on a statistics project. 
%	}
%	
	
	
	
	\section{Volunteering}
	
	\cventry{2016-2019}{Outreach volunteer}{University of Sydney}{}{}{ Delivered seminars and hands-on workshops for visiting high school and university students.
%		\begin{itemize}
%			%		\item Long-term participant of the outreach program at the School of Mathematics and Statistics. 
%%			\item 
%%			\item Previously a board member of the School Outreach committee.
%			%		A short abstract of my research on the USYD website is  \href{https://sydney.edu.au/science/news-and-events/2018/12/13/4-cool-topics-you-can-study-in-maths.html?fbclid=IwAR3I3pYHL-yBls__Rt0izDf_wguMjVVEIiK26Vu58j6XneF1Ixn5ZjZhbMk}{here}.
%		\end{itemize}
	}
	
	\cventry{2017}{President}{Sydney University Mathematics Society}{}{}{ Oversaw finances of the Society, organised academic/industry events and and negotiated coporate sponsorships for three years.
%		\begin{itemize}
%			\item 
%			\item Organising speakers for industry and academic seminars and social events. 
%			\item Management of social media accounts, operations and sales of merchanise.
			%		\item Previous positions held: Vice President, Treasurer and Social Director. 
			%\item Oct 2016 - \emph{``Primes, Poisson, and Pok\'{e}mons."}
			%\item Oct 2016 - \emph{``The Pok\'{e}mon Collector's Problem: A Simulation Study Based on Theoretical Modesl and Applied Methods."}
			%\item Aug 2015 - \emph{``An Application of PCA to Cricket Data and General Practice of Statistics''}
			%\item Apr 2015 - \emph{``Model Selection and Model Averaging --- Danger of Certainty in Statistics''}
			%\item May 2014 - Presentation on \emph{``An Algorithm To Achieve Optimality And Stability of Marriages and College Admission.''}
%		\end{itemize}
	}
	
	
	\cventry{2015}{President}{Sydney University Statistics Society}{}{}{Organised academic/industry events and and negotiating coporate sponsorships.
%		\begin{itemize}
%			\item 
			%\item April 2015: organising introductory SAS software workshop. 
			%\item In September 2015, we invited founder of Prioma Capitals for careers talk. 
%		\end{itemize}
	}
	
	\section{Awards}
	\cventry{2019}{Statistical Society of Australia}{JB Douglas Award (joint runner-up). Prize awarded to the top statistics reseach PhD students in New South Wales. AUD 250}{}{}{}
	\cventry{2019}{Statistical Society of Australia}{Golden Jubilee Travel Grant. Competitive funding for a statistics PhD student in Australia. AUD 1,000}{}{}{}
	\cventry{2018}{Sydney Bioinformatics Research Symposium}{Best poster student presentation at the conference. AUD 50}{}{}{}
	\cventry{2017}{International Biometric Society -  Australasian Region}{Best student talk at the conference. AUD 500}{}{}{}
	\cventry{2017 \& 2018 }{Australian Bioinformatics \& Computational Biology Society}{Travel scholarship to ABACBS annual conference. AUD 250}{}{}{}
	\cventry{2016-2019}{Australian Postgraduate Award}{For the duration of PhD program at the University of Sydney. AUD 26,288 p.a}{}{}{}
	\cventry{2015}{International Biometric Society - Australasian Region}{Awarded to the top biostatistics student undertaking a Honours program. AUD 1,500}{}{}{}
	

\newpage
	\section{Publications}
	
	
\cvitem{\thepublishcount}{Lin, C., \textbf{Wang, K. Y. X.}, \& Mueller, S. \textbf{2020}. mcvis: A new framework for collinearity discovery, diagnostic and visualization. Journal of Computational and Graphical Statistics, In Press.}	

\cvitem{\stepcounter{publishcount} \thepublishcount}{Hewavisenti, R., Ferguson, A., \textbf{Wang, K. Y. X.}, Jones, D., Gebhardt, T., Edwards, J., Zhang, M., Britton, W., Yang, J., Hong, A., \& Palendira, U. (2020). CD103+ tumour-resident CD8+ T cell numbers underlie improved patient survival in oropharyngeal squamous cell carcinoma. Journal for ImmunoTherapy of Cancer, In Press}

\cvitem{\stepcounter{publishcount} \thepublishcount}{\textbf{Wang, K.Y.X.}, Tarr, G., Yang, J.Y.H., Mueller, S. \textbf{2019}. Fast and approximate exhaustive variable selection for generalised linear models with APES,  Invited paper to \textit{Australia \& New Zealand Journal of Statistics}, 61 (4) 445-465.}

\cvitem{\stepcounter{publishcount} \thepublishcount}{
	Lin, Y., Ghazanfar, S., \textbf{Wang, K.Y.X.}, Gagnon-bartsch, J.A., Lo, K.K., Han, Z., Ormerod, J.T., Speed, T.P., Yang, P., Yang, J.Y.H. \textbf{2019}. scMerge: Leveraging factor analysis, stable expression and pseudo-replication to merge multiple single-cell RNA-seq data, \textit{Proceedings of the National Academy of Sciences of the United States of America}, 116 (20) 9775-9784.}	

\cvitem{\stepcounter{publishcount} \thepublishcount}{Pires da Silva, I., \textbf{ Wang, K.Y.X.}, Wilmott, J.S., Holst, J., Carlino, M.S., Park, J.J., Quek, C., Wongchenko, M., Yan, Y., Mann, G., Johnson, D.B., McQuade, J.L., Rai, R., Kefford, R.F., Rizos, H., Scolyer, R.A., Yang, J.Y.H., Long, G. V, Menzies, A.M. \textbf{2019}. Distinct molecular profiles and immunotherapy treatment outcomes of V600E and V600K BRAF-mutant melanoma. \textit{Clinical Cancer Research}, 25 (4) 1272-1279.}


\cvitem{\stepcounter{publishcount} \thepublishcount}{\textbf{Wang, K.Y.X}., Menzies, A.M., Silva, I.P., Wilmott, J.S., Yan, Y., Wongchenko, M., Kefford, R.F., Scolyer, R.A., Long, G. V, Tarr, G., Mueller, S., Yang, J.Y.H. \textbf{2019}. bcGST - an interactive bias-correction method to identify over-represented gene-sets in boutique arrays. \textit{Bioinformatics}, 35 (8) 1350-1357.}

\cvitem{\stepcounter{publishcount} \thepublishcount}{Strbenac, D., \textbf{Wang, K.Y.X.}, Wang, X., Dong, J., Mann, G.J., Mueller, S., Yang, J.Y.H. \textbf{2019}. Melanoma Explorer: a web application to allow easy reanalysis of publicly available and clinically-annotated melanoma omics datasets. \textit{Melanoma Research}.}
	%
	
	
	%\cvitem{\LaTeX}{Highly proficient. Written extensive university materials using \LaTeX. Designed and delivered workshop for university  undergraduates.}
	%\cvitem{Mathematica\\MATLAB/Julia \\ Tablaeu}{Working knowledge.}
	

	
	%----------------------------------------------------------------------------------------
	
	
	
	%----------------------------------------------------------------------------------------
	%	LANGUAGES SECTION
	%----------------------------------------------------------------------------------------
	%\clearpage
	
	%\section{Miscellaneous}
	%
	%
	%\section{Professional society memberships}
	%\cvitem{}{
	%\begin{itemize}
	%\item Australian Bioinformatics \& Computational Biology Society
	%\item International Biometric Society (Australasian Region)
	%\item Royal Statistical Society
	%\item Statistical Society of Australia
	%%\item International Educational Data Mining Society. 
	%\end{itemize}
	%}
	
	
	
	%
	\section{Presentations}
	\cvitem{Workshop}{
	\begin{itemize}
		\item \textit{"Single-cell RNA-Seq analysis from beginning to end"} at Hong Kong University (2019), Sydney University (2019) and Cornell University (2020).
		\item \textit{"Enter the Tidyverse with R and RStudio"} at BioinfoSummer (2019).
		\item \textit{"Fast algorithms and modern visualisations for feature selection"} at Joint International Society for Clinical Biostatistics and Australian Statistical Conference (2018). 
	\end{itemize}
	}

	
	\cvitem{Talks}{
	\begin{itemize}
		\item 2019 International Conference on Econometrics and Statistics (invited)
		\item 2019, 2017 International Biometrics Society - Australasian Region Conference
		\item 2018 Australian Bioinformatics \& Computational Biology Society Conference
		\item 2018 Joint Statistical Meeting
		\item 2017 International Conference in Robust Statistics 
		\item 2016 Australian Statistical Conference
	\end{itemize}		
	}
	
	
%\section{Teaching}
%\hspace{2.6cm} Courses are listed below with lecturing duties highlighted in \textbf{bold}: \\ 
%\cvitem{Undergraduate}{DATA1001: Foundation of Data Science (\textbf{2018 S2})}
%	\cvitem{}{DATA1901: Foundation of Data Science (Adv) (2019 S1)}
%	\cvitem{}{DATA2902:  Learning from Data (Adv) (2019 S2)} 
%	\cvitem{}{MATH1001: Differential Calculus (2016 S1)}
%	\cvitem{}{MATH1005: Statistics (\textbf{2015 WS}, S2; 2016 SS, WS; \textbf{2017 S2}, SS)
%	}
%	\cvitem{}{MATH1015: Statistics (2015 S1, \textbf{2018 S1})
%	}
%	\cvitem{}{MATH1115: Interrogating Data (2019 S1)}
%	\cvitem{}{MATH1905: Statistics (Adv) (2016 S2)
%	}
%	\cvitem{}{MATH2069: Discrete Mathematics and Graph Theory (2016 S1)
%	}
%	\cvitem{}{PHAR1811: Foundation of Pharmacy (2016 S1)
%	}
%	\cvitem{}{PHAR2813: Therapeutic Principles (2016 S1)
%	}
%	\cvitem{}{STAT2911: Probability Theory (Adv) (2017 S1)
%	}
%	\cvitem{}{STAT2912: Statistical Tests (Adv) (2016 S2)
%	}
%	\cvitem{}{STAT3914: Applied Statistics (Adv) (\textbf{2016 S2})
%	}
%	
%	\cvitem{Postgraduate}{STAT5002: Introduction to Statistics (2017 S1; \textbf{2018 S1})
%	}
%	\cvitem{}{STAT5003: Computational Statistical Methods (2016 S2; \textbf{2017 S2})
%	}
	
	
	
	
%	\cvitem{Poster}{
%		\begin{itemize}
%			\item 2016, 2017, 2018 Sydney Bioinformatics Research Symposium
%			\item 2016, 2017 Australian Bioinformatics \& Computational Biology Society Conference 
%			\item 2016 Sydney Cancer Conference
%			\item 2015 AMSI BioInfo Summer
%		\end{itemize}	
%	}


%	
%	\cventry{2012-2013}{Mathematics Special Studies Program(SSP)}{}{}{}{
%	Invited into the prestigious SSP in University of Sydney. These are special courses for selected students to learn about advanced topics and develop professional mathematical communication and presentation skills.
%	\begin{itemize}
%	\item MATH2917 Project: Proof of Alternating Matrices Conjecture --- Jacobi's Triple Product Identity and Euler's Pentagonal Number Theorem, Ramanujan's Congruences of Partition Function. \url{http://goo.gl/tUkCAe}
%	\item MATH2916 project: Calculus of Variation --- Optimizations and Isoperimetric Constraints on Functionals. \url{http://goo.gl/3VcbZN}
%	\end{itemize}
%	}
	
	
	%
	%\section{Miscellaneous}
	%\cvitem{Language}{English, Mandarin, Cantonese}
	%
	%\cvitem{Citizenship}{
	%Australian citizen
	%}
	
	
	
	
	
	%----------------------------------------------------------------------------------------
	%	INTERESTS SECTION
	%----------------------------------------------------------------------------------------
	
	%----------------------------------------------------------------------------------------
	%	COVER LETTER
	%----------------------------------------------------------------------------------------
	
	% To remove the cover letter, comment out this entire block
	
	%\clearpage
	%
	%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
	%\date{\today} % Letter date
	%\opening{Dear Sir or Madam,} % Opening greeting
	%\closing{Sincerely yours,} % Closing phrase
	%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
	%
	%\makelettertitle % Print letter title
	%
	%\lipsum[1-3] % Dummy text
	%
	%\makeletterclosing % Print letter signature
	
	%----------------------------------------------------------------------------------------
	
\end{document}