 \documentclass[12pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
%/usr/local/texlive/2015/texmf-dist/tex/latex/moderncv

\newcounter{publishcount}
\stepcounter{publishcount}

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.8]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Kevin YX} % Your first name
\familyname{Wang} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Room 807, School of Mathematics and Statistics, Carslaw Building (F07)}{University of Sydney, NSW, Australia 2006}
\mobile{(+61) 404 955 255}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{kevin.wang@sydney.edu.au}
\homepage{https://kevinwang09.github.io/}{} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{https://github.com/kevinwang09. Updated on \today}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2016--2019}{Doctor of Philosophy in Science}{University of Sydney}{}{}{A statistical framework for incorporating multi-omics technologies for precision medicine. Supervised by Prof.\ Jean Yang, Prof.\ Samuel M\"{u}ller and Dr.\ Garth Tarr.}

\cventry{2012-2015}{Bachelor of Science (Adv. Mathematics) (Hon. I)}{University of Sydney}{}{}{Major in Statistics and Financial Mathematics. \\ Honours thesis: Biostatistics - Examination of appropriate measures of association to resting-state fMRI data. Supervised by Prof. Jean Yang and Dr. John Ormerod.} 

\section{Professional experience}
\cventry{2019--2020}{Research Associate}{University of Sydney}{}{}{
	\begin{itemize}
		\item Project outline: developing a clinically implementable prediction model using omics data, particularly for melanoma.
		\item 1.0 FTE between October 2019 to Feburary 2020. 
	\end{itemize}	
}

\cventry{2016--2019}{Postgraduate Teaching Fellow}{University of Sydney}{}{}{
\begin{itemize}
	\item Writing engaging and informative lecturing materials for courses at both undergraduate and postgraduate level. Deliver lectures and tutorials to classes up to 200 students. Writing assessments and performing administrative tasks. Providing consultation time for students and mentoring new tutors. 0.2 FTE. 
\end{itemize}	
}




%		\begin{itemize}
%	\item MATH1001: Differential Calculus
%	\item MATH1005: Statistics (four times)
%	\item MATH1015: Biostatistics 
%	\item MATH1905: Statistics (Advanced)
%	\item MATH2069: Discrete Mathematics and Graph Theory
%	\item PHAR1811: Foundation of Pharmacy (Statistics copmonent)
%	\item PHAR2813: Therapeutic Principles (Mathematics and Statistics components)
%	\item STAT2911: Probability Theory (Advanced)
%	\item STAT2912: Statistical Tests (Advanced)
%	\item STAT3914: Applied Statistics (Advanced)
%	\item STAT5002: Introduction to Statistics (Master of IT core component)
%	\item STAT5003: Computational Statistical Methods (Master of IT core component)
%	\end{itemize} 





\cventry{2016}{Charles Perkins Centre Summer Research Scholarship in Bioinformatics}{University of Sydney}{}{}{
\begin{itemize}
\item \textit{A Shiny implementation for differential variability analysis via a network approach}. Supervised by Prof. Jean Yang and Prof. Graham Mann.  
\end{itemize} 
}



%\cventry{2015-2016}{University Statistics Tutor}{The University of Sydney}{}{}{
%\begin{itemize}
%%\item 2015 Sem 1: MATH1015 - Biostatistics Class.
%%\item 2015 Winter School, Sem 2, 2016 Summer School: MATH1005 - Statistics Class Tutor.
%\item Later promoted to the position of Postgraduate Teaching Fellow at the School. 
%\end{itemize}
%}





\cventry{2015}{Summer Research Scholarship in Mathematical Statistics}{Australian National University}{}{}{
\begin{itemize}
\item \textit{Frequentist model selection and model averaging techniques}. Supervised by Prof.\ Alan Welsh. 
%\item Participated in 3 Minutes Thesis competition in Burgmann College, ANU.
%\item Value: 1000 AUD + 2 months of full time accomodation.
%\item Abstract: Model averaging attempts to account for model selection uncertainty by considering a set of different models. It is closely related to the classical model selection. Both techniques were studied using simulated data in this project. 
\end{itemize} 
}




\cventry{2013}{Winston Charitable Foundation Internship in Mathematical Biology}{University of Sydney}{}{}{
\begin{itemize}
\item \textit{Spread of the Varroa Mite among different castes of honey bee hives}. Supervised by Prof. Mary R Myerscough.
%\item \textit{Mathematica} modeling of differential equations that govern the spread fo Varroa mites in a bee hive. The most important features tested were the existence of equilibria and effects of several parameters on natural recovery.  
\end{itemize}
}

\section{Professional service}


\cventry{2016-Present}{Outreach volunteer}{University of Sydney}{}{}{
	\begin{itemize}
		\item Long-term participant of the outreach program at the School of Mathematics and Statistics. Currently a board member of the School Outreach committee and a Virtual Visitor for high school students. Designed various hands-on workshop activities for students. 
%		A short abstract of my research on the USYD website is  \href{https://sydney.edu.au/science/news-and-events/2018/12/13/4-cool-topics-you-can-study-in-maths.html?fbclid=IwAR3I3pYHL-yBls__Rt0izDf_wguMjVVEIiK26Vu58j6XneF1Ixn5ZjZhbMk}{here}.
	\end{itemize}
}

\cventry{2013-2017}{President}{Sydney University Mathematics Society}{}{}{
	\begin{itemize}
		%\item Key responsibilities: 
		%	\begin{itemize}
		%		\item Oversee finances of the Society and negotiating coporate sponsorships.
		%		\item Facilitating speakers for career and academic seminars.
		%		\item Collaborations with coporate and student organisations on social events.
		%		\item Management of social media accounts, operations and sales. 
		%	\end{itemize}
		% Including Optiver and Jane Street. 
		\item Hosting mathematical workshops, seminars and outreach activities relating Mathematics and Statistics for the Society and the University. Mentoring students from disadvantaged backgrounds. 
		%\item Previous positions held: Vice President, Treasurer and Social Director. 
		%\item Oct 2016 - \emph{``Primes, Poisson, and Pok\'{e}mons."}
		%\item Oct 2016 - \emph{``The Pok\'{e}mon Collector's Problem: A Simulation Study Based on Theoretical Modesl and Applied Methods."}
		%\item Aug 2015 - \emph{``An Application of PCA to Cricket Data and General Practice of Statistics''}
		%\item Apr 2015 - \emph{``Model Selection and Model Averaging --- Danger of Certainty in Statistics''}
		%\item May 2014 - Presentation on \emph{``An Algorithm To Achieve Optimality And Stability of Marriages and College Admission.''}
	\end{itemize}
}


\cventry{2014-2015}{President}{Sydney University Statistics Society}{}{}{
	\begin{itemize}
		\item Established the Statistics Society in 2014. Responsible for all social and career events during 2015, including an industry workshop with SAS. 
		%\item April 2015: organising introductory SAS software workshop. 
		%\item In September 2015, we invited founder of Prioma Capitals for careers talk. 
	\end{itemize}
}



\section{Honours and Awards}
\cventry{2019}{Statistical Society of Australia}{Golden Jubilee Travel Grant. To fund international conference attendance in 2019. AUD 1,000}{}{}{}
\cventry{2016-Present}{Australian Postgraduate Award}{For duration of the PhD program at the University of Sydney. AUD 26,288 p.a}{}{}{}
\cventry{2018}{Sydney Bioinformatics Research Symposium}{Best poster presentation. AUD 50}{}{}{}
\cventry{2017}{International Biometric Society -  Australasian Region Conference}{Best student talk. AUD 500}{}{}{}
\cventry{2017 \& 2018 }{Australian Bioinformatics \& Computational Biology Society}{Travel scholarship to ABACBS annual conference. AUD 250}{}{}{}
\cventry{2015}{International Biometric Society - Australasian Region}{Honours Scholarship for biostatistics students. AUD 1,500}{}{}{}


\section{Publications}

%\cventry{}{Bioinformatics}{}{}{}{
%	\begin{itemize}
%		\item bcGST - an interactive bias-correction method to identify over-represented gene-sets in boutique arrays
%		Kevin YX Wang, et.\,al.\,2018,
%		bioRxiv 240234; doi: https://doi.org/10.1101/240234
%	\end{itemize}
%}


\cvitem{\thepublishcount}{
	Lin, Y., Ghazanfar, S., \textbf{Wang, K.Y.X.}, Gagnon-bartsch, J.A., Lo, K.K., Han, Z., Ormerod, J.T., Speed, T.P., Yang, P., Yang, J.Y.H. \textbf{2019}. scMerge: Leveraging factor analysis, stable expression and pseudo-replication to merge multiple single-cell RNA-seq data, \textit{Proceedings of the National Academy of Sciences of the United States of America}.}	

\cvitem{\stepcounter{publishcount} \thepublishcount}{Pires da Silva, I., \textbf{ Wang, K.Y.X.}, Wilmott, J.S., Holst, J., Carlino, M.S., Park, J.J., Quek, C., Wongchenko, M., Yan, Y., Mann, G., Johnson, D.B., McQuade, J.L., Rai, R., Kefford, R.F., Rizos, H., Scolyer, R.A., Yang, J.Y.H., Long, G. V, Menzies, A.M. \textbf{2019}. Distinct molecular profiles and immunotherapy treatment outcomes of V600E and V600K BRAF-mutant melanoma. \textit{Clinical Cancer Research} (25) (4) 1272-1279.}


\cvitem{\stepcounter{publishcount} \thepublishcount}{\textbf{Wang, K.Y.X}., Menzies, A.M., Silva, I.P., Wilmott, J.S., Yan, Y., Wongchenko, M., Kefford, R.F., Scolyer, R.A., Long, G. V, Tarr, G., Mueller, S., Yang, J.Y.H. \textbf{2019}. bcGST - an interactive bias-correction method to identify over-represented gene-sets in boutique arrays. \textit{Bioinformatics} (35) (8) 1350-1357.}

\cvitem{\stepcounter{publishcount} \thepublishcount}{Strbenac, D., \textbf{Wang, K.Y.X.}, Wang, X., Dong, J., Mann, G.J., Mueller, S., Yang, J.Y.H. \textbf{2018}. Melanoma Explorer: a web application to allow easy reanalysis of publicly available and clinically-annotated melanoma omics datasets. \textit{Melanoma Research}.}

\cvitem{\stepcounter{publishcount} \thepublishcount}{\textbf{Wang, K.Y.X.}, Tarr, G., Yang, J.Y.H., Mueller, S. \textbf{2019}. Fast and approximate exhaustive variable selection for generalised linear models with APES,  Invited paper to \textit{Australia \& New Zealand Journal of Statistics} (in press).}



\section{Computational skills}
\cvitem{\texttt{R}}{Extremely proficient in writing research level scripts. Professional in using \texttt{tidyverse}, RMarkdown and Shiny. Author of the \texttt{scMerge} Bioconductor package as well as the \texttt{APES} and \texttt{mcvis} packages. Designed and delivered workshops for both industry and academic professionals.}

\cvitem{\texttt{git}}{Highly proficient. Experiences in \texttt{R} package development with unit testing, continuous integration and coverage testing.}

\cvitem{\texttt{docker}}{Working knowledge in building docker images. I hosted academic workshops for 30+ attendees through Google Cloud and received an Google Cloud for Education grant worth \$2,000.}

\cvitem{\texttt{python}}{Working knowledge in writing basic scripts. The R \texttt{mcvis} package is the result of the integration of \texttt{R} and a \texttt{python} script.}

%\cvitem{\LaTeX}{Highly proficient. Written extensive university materials using \LaTeX. Designed and delivered workshop for university  undergraduates.}
%\cvitem{Mathematica\\MATLAB/Julia \\ Tablaeu}{Working knowledge.}


\section{Teaching experiences}

\cvitem{}{
	I have lectured 6 and tutored 15 courses at the University of Sydney, spanning statistics, mathematics, pharmacy, and machine learning at both undergraduate and postgraduate levels with strong positive student feedback. In addition, I have supervised one exchange student on a computational statistics project. Subjects taught are listed below with lecturing roles bolded.
}

\cvitem{Undergraduate}{DATA1001: Foundation of Data Science (\textbf{2018 S2})}
\cvitem{}{DATA1901: Foundation of Data Science (Advanced) (2019 S1)}
\cvitem{}{MATH1001: Differential Calculus (2016 S1)}
\cvitem{}{MATH1005: Statistics (\textbf{2015 WS}, S2; 2016 SS, WS; \textbf{2017 S2}, SS)
}
\cvitem{}{MATH1015: Statistics (2015 S1, \textbf{2018 S1})
}
\cvitem{}{MATH1115: Interrogating Data (2019 S1)}
\cvitem{}{MATH1905: Statistics (Advanced) (2016 S2)
}
\cvitem{}{MATH2069: Discrete Mathematics and Graph Theory (2016 S1)
}
\cvitem{}{PHAR1811: Foundation of Pharmacy (2016 S1)
}
\cvitem{}{PHAR2813: Therapeutic Principles (2016 S1)
}
\cvitem{}{STAT2911: Probability Theory (Advanced) (2017 S1)
}
\cvitem{}{STAT2912: Statistical Tests (Advanced) (2016 S2)
}
\cvitem{}{STAT3914: Applied Statistics (Advanced) (\textbf{2016 S2})
}

\cvitem{Postgraduate}{STAT5002: Introduction to Statistics (2017 S1; \textbf{2018 S1})
}
\cvitem{}{STAT5003: Computational Statistical Methods (2016 S2; \textbf{2017 S2})
}


%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
%\clearpage

%\section{Miscellaneous}


%\cventry{2014}{Private University Tutoring}{}{}{}{
%During 2014, I am helping to improve the performance of 1st year university students in statistics.}


%\cventry{2012-2015}{The Brain Education-High School Maths Tutor}{}{}{}{
%Since 2012, I tutored numerous high school students both privately and within coaching schools, including the Brain Education. I have written extensive teaching materials in \LaTeX. 
%}

\section{Professional society memberships}
\cvitem{}{
\begin{itemize}
\item Australian Bioinformatics \& Computational Biology Society
\item International Biometric Society (Australasian Region)
\item Royal Statistical Society
\item Statistical Society of Australia
%\item International Educational Data Mining Society. 
\end{itemize}
}

\section{Presentations}
\cvitem{Workshop}{
\begin{itemize}
	\item 2019 December - BioinfoSummer hosted by Australian Mathematical Science Institute. Invited workshop instructor for \textit{"Enter the Tidyverse with R and RStudio"}
	\item 2019 November - Charles Perkins Centre, University of Sydney.  \textit{"Single-cell RNA-Seq analysis from beginning to end"}
	\item 2019 June -  Hong Kong University. Invited workshop instructor for \textit{"Single-cell RNA-Seq analysis using} \texttt{scMerge}\textit{"}
	\item 2018 September - Joint International Society for Clinical Biostatistics and Australian Statistical Conference. Invited workshop instructor for \textit{"Fast algorithms and modern visualisations for feature selection"}
\end{itemize}
}

\cvitem{Invited talk}{
	\begin{itemize}
		\item 2019 International Conference on Econometrics and Statistics
	\end{itemize}
}

\cvitem{Contributed talks}{
\begin{itemize}
	\item 2019, 2017 International Biometrics Society - Australasian Region Conference
	\item 2018 Australian Bioinformatics \& Computational Biology Society Conference
	\item 2018 Joint Statistical Meeting
	\item 2017 International Conference in Robust Statistics 
	\item 2016 Australian Statistical Conference
\end{itemize}		
}

\cvitem{Poster}{
	\begin{itemize}
		\item 2016, 2017, 2018 Sydney Bioinformatics Research Symposium
		\item 2016, 2017 Australian Bioinformatics \& Computational Biology Society Conference 
		\item 2016 Sydney Cancer Conference
		\item 2015 AMSI BioInfo Summer
	\end{itemize}	
}

%\cventry{2012-2013}{Mathematics Special Studies Program(SSP)}{}{}{}{
%Invited into the prestigious SSP in University of Sydney. These are special courses for selected students to learn about advanced topics and develop professional mathematical communication and presentation skills.
%\begin{itemize}
%\item MATH2917 Project: Proof of Alternating Matrices Conjecture --- Jacobi's Triple Product Identity and Euler's Pentagonal Number Theorem, Ramanujan's Congruences of Partition Function. \url{http://goo.gl/tUkCAe}
%\item MATH2916 project: Calculus of Variation --- Optimizations and Isoperimetric Constraints on Functionals. \url{http://goo.gl/3VcbZN}
%\end{itemize}
%}






\section{Miscellaneous}
\cvitem{Language}{
\begin{itemize}
\item English 
\item Mandarin
\item Cantonese
\end{itemize}
}

\cvitem{Citizenship}{
	\begin{itemize}
		\item Australian citizen
	\end{itemize}
}





%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-3] % Dummy text
%
%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}